\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{casual}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\firstname{Lev}
\familyname{Babchenko}
\email{lvbabchenko@gmail.com}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\nopagenumbers{}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Computer skills}
\cvcomputer{Languages}{Go, C/C++, Python, Bash, \\
                       SQL, PL/PgSQL}
           {Operation Systems}{Linux, Windows, OpenVMS, z/OS}
\cvcomputer{Databases}{PostgreSQL, MongoDB, SQLite, \\
                       YQL/YT,\\
                       DB2 UDB (SQL, API, Low-Level)}
           {Tools/Libs}{uServer, AWS, Docker, Docker-Compose, git}

\section{Languages}
\cvlanguage{Russian}{Native}{}
\cvlanguage{English}{Intermediate}{}

\section{Work Experience}
% \subsection{Vocational}
\cventry{2023-now}{Senior Software Engineer}{Teracloud Inc.}{Copenhagen}{}{OpenVMS: System Development}
\cventry{2022-2023}{Senior Software Engineer}{Energy Machines Inc.}{Copenhagen}{}{OpenVMS: System Development; TeraBlast: GoLang Development}
\cventry{2020-2022}{Lead Developer}{TeraCloud Rus.}{Saint-Petersburg}{}{OpenVMS: System Development; TeraBlast: GoLang Development}
\cventry{2018-2020}{Developer}{Yandex LLC.}{Saint-Petersburg}{}{Yandex Taxi Backend Development}
\cventry{2015--2018}{Developer}{Applied Technologies, Ltd.}{Chelyabinsk}{}{QMF for z/OS Development}
\cventry{2011--2015}{Developer}{3DIVI Company}{Chelyabinsk}{}{software development for Computer Vision Systems}
\cventry{2009--2011}{System \& DB Administrator}{Applied Technologies, Ltd.}{Chelyabinsk}{}{project for financical analysis and prognosis}
\cventry{2004--2009}{Senior Programmer}{TG Telecom, Ltd.}{Chelyabinsk}{}{software development for distributed payment system}
\cventry{2003--2009}{Senior Programmer}{Applied Technologies, Ltd.}{Chelyabinsk}{}{development of system for data auditing/recovery for IBM DB2}
\cventry{1999--2003}{Senior Programmer}{Business High School}{Chelyabinsk}{}{development of system for data management for IBM DB2}
\cventry{1996--1999}{Software Developer}{ZAO "Nedra"}{Chelyabinsk}{}{geographic information system development}
\cventry{1992--1996}{Software Developer}{Department of Security by Kurchatovsky District}{Chelyabinsk}{}{software development for security system}
\cventry{1992--1992}{Software Developer}{Regional Narcological Dispensary}{Chelyabinsk}{}{development of expert system for internal enterprise usage}
% \subsection{Miscellaneous}

\section{Projects}

\cventry{2022-now}{Teracloud Inc}{}{}{}{ACMEVMS. System component for authorizarion and authentication}
\cventry{2020-2022}{TeraCloud Rus., Energy Machines Inc.}{}{}{}{Feed Distribution. Streaming Solution for BlastPremier}
\cventry{2020}{TeraCloud Rus.}{}{}{}{BASH Port for OpenVMS}
\cventry{2020}{TeraCloud Rus.}{}{}{}{GNV (GNU Toolset for OpenVMS)}

\cventry{2018-2020}{taxi-backend}{}{}{}{Yandex.Taxi Backend services, billing subsystem}

\cventry{2015-2018}{QMF Z Client}{}{}{}{z/OS Client for DB2}

\cventry{2011--2015}{Sphinx}{}{}{}{Automate Surveillance System}
\cventry{2011--2015}{SkiRacer}{}{}{}{Automated video recording system for Sport}
\cventry{2013--2014}{Papillon Live Scanner}{}{}{Papillon Systems}{System for Electronic Fingerprinting}
\cventry{2013--2015}{Seemetrix}{}{}{}{Anonimous Face Analysis \& Audience Analytics Solution}

\cventry{2010--2011}{TGPay2}{}{}{TG Telecom, Ltd.}{distributed payment system, successor of TGPay}
\cventry{2009--2011}{Tracker.KCN}{}{}{TG Telecom, Ltd.}{ERP\&CRM System}
\cventry{2005--2010}{TGPay}{}{}{TG Telecom, Ltd.}{distributed payment system}

\cventry{2002--2009}{Recovery Expert for Multiplatforms}{}{}{Rocket Software, Inc.}{Auditing and Recovery Toolset for DB2}
\cventry{1999--2002}{QMF for Windows/Rocket Shuttle}{}{}{Rocket Software, Inc.}{Advanced Query/Report Viewer for DB2}
\cventry{1999--1999}{TreeDB}{Business High School}{Chelyabinsk}{}{Hierarhical Database}

\cventry{1997--1998}{NedraGIS}{}{}{ZAO "Nedra"}{geographic information system}
\cventry{1997--1998}{GISImport}{}{}{ZAO "Nedra"}{data convertor/importer for NedraGIS}
\cventry{1997--1998}{GISPic}{}{}{ZAO "Nedra"}{semi-automatic manager/vectorizer for large bitmaps}

\cventry{1995--1997}{RCSS}{}{}{Department of Security by Kurchatovsky District}{Software for control panel and server of centralized R/C security system}
\cventry{1995--1997}{NetBackup}{}{}{Department of Security by Kurchatovsky District}{Network backup system}

\end{document}
%% end of file
